### 2015-06-08 publishing/response-to-reviewers.md
added first manuscript and started revision

PONE-D-15-17915
3D-Printed 24-Well Plate Oxygen Control Device
PLOS ONE

Dear Arum Han and reviewers,

Thank you for reviewing our manuscript submission to PLOS ONE. We have made several improvements and clarifications resulting what we hope is a stronger manuscript ready for publication.

If you would like to make changes to your financial disclosure, please include your updated statement in your cover letter.

In addition to this rebuttal letter a clean revised manuscript is submitted as well as a marked-up copy with tracked changes.

Yours sincerely,

David Eddington, Ph.D.
University of Illinois at Chicago

Authors' Rebuttal to Reviewers

Reviewer #1:
It is a different version of design to control oxygen in cell culture, among some recent efforts. One concern is that the group has published quite a number of papers on oxygen control devices, although it is now through 3d printing. It is important to highlight in front the key improvements.

Authors' rebuttal:

Also, it is important to compare with some other methods related to 3d printing such as that done recently by Kamei K. et al. (Biomed Microdevices. 2015 Apr;17(2):36).

Authors' rebuttal:

"This is the first 3D-printed device that can be functionalized to control oxygen in cell culture" is a statement which is too strong.

Authors' rebuttal:

------------------------------

Reviewer #2:
Currently, little consideration is given to mimicking physiological oxygen concentrations in vitro during cell experiments. Oftentimes cells are cultured at atmospheric oxygen conditions which are higher than what is found in many tissues, including tumor environments. Some systems have been developed to control the oxygen environment in vitro, but these can be cumbersome or costly to implement. 3D printing has emerged as a rapid prototyping method to fabricate devices with high control over structure and therefore is an attractive method to design a microfluidic device capable of controlling oxygen concentrations in culture. Brennan et al. report on a 3D printed control device capable of adjusting oxygen concentrations in a 24-well plate. Although the concept is interesting, the data is not sufficient and additional experiments are needed to improve the manuscript. 
•	Page 3 - In addition to presenting gap distance below insert and well bottom, it would be helpful if the authors included volume of media this space would hold.

Authors' rebuttal:

•	Page 4 – Why was 6 hrs chosen for cell culture? It would seem that the authors could demonstrate a more robust change in expression over the concentrations tested if the experiment was extended to a longer time point, especially considering only the 0% group showed a significant difference in VEGFA expression.

Authors' rebuttal: VEGFA is under the transcriptional activity of HIF-1alpha. HIF protein peaks at 4 hr, and so we looked at a time point slightly delayed. By longer time points, the HIF response is actually suppressed, and many transcripts are not increased with longer time points. See Rexius-Hall et al.s' work.

•	The authors specify concentrations of 21%, 10%, 5%, and 0% were evaluated, however in their Figure 2b, the concentrations appear closer to 13% (not 10%) and 7% (not 5%). Variation of 3% can be considerable in physiological environments and it is unclear if the authors recognize this variation. It is also amplified by the lack of error bars for each group.

Authors' rebuttal:

•	Is sterilization an issue for this device, considering it will be in close contact with biological components?

Authors' rebuttal:

### 2015-06-23 publishing/latex/revision.tex
added revision tex for latex diff

% Template for PLoS
% Version 3.1 February 2015
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig." instead of "Figure".
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}
\usepackage[version=3]{mhchem}  % added by author

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 250 characters or less.
% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
\begin{flushleft}
{\Large
\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device - Submission to PLOS ONE}
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Martin D. Brennan\textsuperscript{1},
Megan L. Rexius-Hall\textsuperscript{1},
David T. Eddington\textsuperscript{1,*},
\\
\bigskip
\bf{1} Dept of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
\\
\bigskip

% Use the asterisk to denote corresponding authorship and provide email address in note below.
* dte@uic.edu

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to oxygen-impermeable materials.
We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D-printed microfluidic devices as a means to enable oxygen control cell culture studies.
The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on a 24-well oxygen control device for standard multiwell plates.
The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
With this device, four different oxygen conditions were able to be controlled, and six wells were maintained under each oxygen condition. 
We demonstrate enhanced transcription of the gene VEGFA (vascular endothelial growth factor A) with decreasing oxygen levels in human lung adenocarcinoma cells.
This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.

\linenumbers

\section*{Introduction}
Here we report on the development of 3D-printed microfluidic devices for the control of oxygen in cell culture microenvironments.
We demonstrate a device that nests into a 24-well culture plate to control gas in each row of the plate independently of the incubator's condition.
This expands on our previous work of a device fabricated using PDMS molds and planar lithography for 6-well plates\cite{Oppegard2009,Oppegard2010}.
The ability to independently control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.

3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques\cite{Waldbaur2011,Chen2014a}.
In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$200/device \cite{Au2014}.
3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014,Comina2014, Chen2014,Shallan2014,Bhargava2014}. 
Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{ Au2014, Shallan2014} including modular re-configurable units\cite{Yuen2008,Bhargava2014,Lee2014}.
3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012,Kitson2013,Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}. 
Other 3D-printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.

Printing is currently limited in choice of substrate compatible with the 3D printing process.
Substrate options include many proprietary formulations which have been successfully used in a variety of applications.
New techniques for using 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a,Kamei2015} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
To date, there are no widely available methods or materials to facilitate direct printing of gas-permeable materials, although this area is actively being explored\cite{Femmer2014a}.
Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to its biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.

Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
Typically cell culture studies are performed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
For example, tumors are generally hypoxic as cancer cells rapidly outgrow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy\cite{Vaupel2004,Vaupel2007,Gilkes2014}.
Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors\cite{Ke2006,Semenza1999,Semenza2002}.
To better study the role of oxygen levels in cancer gene expression, a gas controlled culture system is required.

Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the shelf well plate \cite{Oppegard2009, Oppegard2010}.
These devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
In addition, tubing was used to connect each pillar which became quite cumbersome when moving to a newer 24-well version.
Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels to eliminate the connection tubings between wells and hose barbs for better tubing connections, while eliminating fabrication time and failure rate.
Although available 3D printable materials are gas-impermeable, the addition of a PDMS membrane following printing of the passive microfluidic network is a simple addition allowing gas transfer. 
In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer from the bulk material prior to the gas exchange interface.
The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is no longer needed.
Convection and distribution of the gas is done in the impermeable material, eliminating dilution of the gas before reaching the diffusion layer.

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Design of insert}

The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24-well plate. 
The 24-well plate insert was designed to control gas in 4 rows of 6 wells each. 
Each of the 4 rows can be controlled independently from an input and also incorporates an integrated distribution network and hose barbs to simplify device operation.
The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Fig.~\ref{fig1}).
The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Fig.~\ref{fig1}).

\begin{figure}[h]
\caption{
{\bf Design of 24-well Insert Device.}
(A) Rendering of whole 3D printed part.
An inlet and outlet barb allows perfusion of gas to control 6 wells.
(B) At the bottom of each pillar gas entering from the outer channel flows along the PDMS membrane (blue), which is supported by micropillars, and exhausts via the inner pipe.
Diffusion occurs rapidly through the PDMS membrane to the cell culture spaced 500 $\mu$m away at the bottom of the well.
(C) Cross-section demonstrating how the microfluidic distribution network and double pipes are connected. 
The two adjacent mirrored distribution networks are spaced 1 mm apart along the z-axis allowing them to overlap and enter the separate vertical pipes.
The arrows indicate the flow direction.
The incoming gas enters the outer pipe on its way to the bottom of the well and returns through the inner pipe.
(D) Photo of the device with dyed channels in a 24-well plate.
(E) Photo of the device from the bottom with four independent channel networks.
(F) Photo of the printed distribution networks.
}
\label{fig1}
\end{figure}

\subsection*{Fabrication of the insert}

CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas-permeable membrane of PDMS to enable diffusion of gas to the culture area. 
The PDMS membranes were fabricated by spin coating 10:1 PDMS (Sylgard 184) on a silicon wafer at 900 RPM to a thickness of $\sim$100 $\mu$m and curing at $70\,^{\circ}$C for 30 minutes.
The PDMS membrane was cut to size and attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.

\subsection*{Oxygen characterization}

Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
Sensors were prepared as discussed previously \cite{Sinkala2010,Rexius-Hall2014}. 
Briefly, polystyrene was dissolved in toluene to form a solution to which PtOEPK (Frontier Scientific) was mixed in before spin coating to a thin layer and allowing the toluene to evaporate.
The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis.

Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports via a flow meter (FL-5311G; Omega) set at 50 ccm.
The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow rate of 30 ccm which exceed the vacuum flow rate (12.5 ccm per 6-well network) so that the gas of interest was pulled into the inlet rather than room air due to the open connection.
In this way, the pressure, and therefore flow rate, was equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.

Initially the inlets are fed with a 5\% \ce{CO2}, balanced air tank until the intensity stabilized.
The inlets were then switched to the control gas of either 0, 5, 10, or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
Intensity measurements were then taken every five minutes for six hours.
All gas tanks used in the oxygen characterization were 5\% \ce{CO2}  in addition to the desired gas mix in anticipation of cell culture experiments (where \ce{CO2} is necessary to buffer the culture media) as \ce{CO2} can alter the fluorescence of the PtOEPK.
The this entire procedure was repeated three independent times.

\subsection*{Cell culture}

Human lung adenocarcinoma (A549) cells were seeded at 30,000 cells per well in a 24-well plate.
Cells were cultured in DMEM supplemented with 10\% FBS.
After reaching $\sim$70\% confluency, the 24-well insert was placed in the plate and the gases were perfused through the device in the same scheme as in the oxygen characterization.
Each row of six wells experienced either 0\%, 5\%, 10\% or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
The assembly was placed in an incubator at $37\,^{\circ}$C for six hours.

\subsection*{Quantitative PCR}

Following six hours of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
Cells in each well were washed twice with PBS, and 300 $\mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
The lysate from each well was collected as a sample.
RNA was extracted according to the PureLink RNA Mini Kit manufacturer’s instructions.

Synthesis of cDNA was performed using the High-Capacity cDNA Reverse Transcription Kit (Applied Biosystems), and quantitative PCR was carried out on ABI PRISM 700O (Applied Biosystems) in 25 $\mu$L reactions using Taqman Gene Expression Assays.
Beta-2-microglobulin (B2M) served as the endogenous control for calculations of relative gene expression.
Six technical replicates from the 6-well control unit were processed for each of four oxygen conditions (0\%, 5\%, 10\% and 21\% \ce{O2}) in three independent experiments.

\subsection*{Statistical analysis}

Cell culture experiments were repeated three independent times. Data are expressed as the mean $\pm$ SD. One-way ANOVA with Tukey’s multiple comparison post-test performed by Prism 5 (Graphpad) determined significance.

% For figure citations, please use "Fig." instead of "Figure".
%Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

%\begin{enumerate}
%\item{react}
%\item{diffuse free particles}
%\item{increment time by dt and go to 1}
%\end{enumerate}

% Results and Discussion can be combined.
\section*{Results}
\subsection*{Oxygen control}
Oxygen control in the 24-well insert device was quantified with a platinum-based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24-well plate (Fig.~\ref{fig2}). There was little variation in the oxygen levels measured in each of the 6 wells controlled by a single inlet, demonstrating the distribution network worked effectively.

\begin{figure}[h]
\caption{
{\bf Oxygen Characterization.} 
(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
Error bars are the standard deviation N=3.
(B) Four oxygen conditions are demonstrated in a 24-well plate.
Each 6-well row of the plate can be controlled independently.  
Mean N=3 error bars not included.
}
\label{fig2}
\end{figure}

\subsection*{Bioverifcation}

Oxygen levels of 21\%, 10\%, 5\%, and 0\% were applied to each set of 6 wells in which A549 cells were cultured.
Measurement of relative gene expression confirmed biological responsiveness of cells under the device’s control.
The device’s ability to control the gas environment was demonstrated with hypoxia-induced upregulation of VEGFA mRNA in the A549 cells (Fig.~\ref{fig3}).  Quantitative PCR showed a significant increase in the relative gene expression of VEGFA in wells exposed to 0\% \ce{O2} for 6 hours as compared to 21\% \ce{O2}. Hypoxia-induced alterations in gene expression usually indicate a HIF-transduced hypoxic signal in cells.
When a HIF transcription factor undergoes nuclear translocation, it can initiate transcription of genes by binding to the hypoxia response element (HRE)\cite{Lee2004} on its target genes.
VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions\cite{RohrerBley2011}.

\begin{figure}[h]
\caption{
{\bf PCR Data.}  VEGFA expression in A549 cells after exposure to different oxygen conditions set-up by the insert device. Data are expressed as mean $\pm$ SD, N=3.
}
\label{fig3}
\end{figure}

\subsection*{Discussion}
This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design while improving distribution and interfacing with tubing due to the 3D-printed element.
Oxygen control is performed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
The VEGFA gene expression in A549 cells confirms a biological response using the multi-well insert.

This 3D-printed device improves on our previous design in a number of ways.
First, the fabrication is greatly simplified. 
No microfabrication, PDMS molding or Parylene coating is required.
Additionally, the non-permanent adhesion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
In PDMS devices the layers are bonded permanently via plasma bonding so damage to a membrane is not repairable.
3D-printing also enables higher levels of intricacy without any additional fabrication, allowing us to include the distribution network, overlapping of channels in the z-axis, and the 'pipe within a pipe' design. 
A comparable PDMS device would require several additional microfabricated layers to be manually aligned to reproduce just the distribution network.

Moving forward with additive manufacturing of microfluidic devices is desirable as it will enable highly integrated designs without any additional fabrication.
For this device an in-device gas mixer could allow more conditions in a single plate, perhaps even one per well or even gradients within wells while reducing the number of gas tanks required as inputs.
This design could also be applied to higher format plates such as 96-well plates.

\section*{Conclusion}
3D printing microfluidic chips have been limited to oxygen-impermeable materials.
We demonstrate oxygen control in 3D-printed devices with the addition of a gas permeable PDMS membrane. 
Oxygen control is demonstrated in a 24-well plate and PCR detection of upregulation of VEGFA mRNA in A549 cells shows the device effectively controls oxygen as expected. 
3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication. 
This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated. 
While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make an injection mold when making tens to hundreds of devices. 
In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is an excellent solution to these device fabrication needs.

%\begin{table}[!ht]
%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
%\caption{
%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
%\begin{tabular}{|l|l|l|l|l|l|l|l|}
%\hline
%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ %\hline
%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ %\hline
%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ %\hline
%\end{tabular}
%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec %pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
%\end{flushleft}
%\label{table1}
%\end{adjustwidth}
%\end{table}

% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}. 
%For more information, see \nameref{S1_Text}.

%\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
%\subsection*{S1 Video}
%\label{S1_Video}
%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. %Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur %pellentesque.

%\subsection*{S1 Text}
%\label{S1_Text}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur %pellentesque.

%\subsection*{S1 Fig}
%\label{S1_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur %pellentesque.

%\subsection*{S2 Fig}
%\label{S2_Fig}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur %pellentesque.

%\subsection*{S1 Table}
%\label{S1_Table}
%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur %pellentesque.

\section*{Acknowledgments}
%This work funded by NSF 1253060.

\nolinenumbers

%\section*{References}
\bibliographystyle{plos2015.bst}
\bibliography{references}

\end{document}

### 2015-06-23 publishing/latex/revision/figures.tex
organized for tracking changes

--- 2015-06-23 publishing/latex/revision.tex
@@
-% Template for PLoS
-% Version 3.1 February 2015
-%
-% To compile to pdf, run:
-% latex plos.template
-% bibtex plos.template
-% latex plos.template
-% latex plos.template
-% dvipdf plos.template
-%
-% % % % % % % % % % % % % % % % % % % % % %
-%
-% -- IMPORTANT NOTE
-%
-% This template contains comments intended 
-% to minimize problems and delays during our production 
-% process. Please follow the template instructions
-% whenever possible.
-%
-% % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Once your paper is accepted for publication, 
-% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
-% the final text of your manuscript.
-%
-% There are no restrictions on package use within the LaTeX files except that 
-% no packages listed in the template may be deleted.
-%
-% Please do not include colors or graphics in the text.
-%
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-%
-% % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- FIGURES AND TABLES
-%
-% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
-%
-% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
-% - Figures should be uploaded separately from your manuscript file. 
-% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
-% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
-% For figure citations, please use "Fig." instead of "Figure".
-% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
-%
-% Tables should be cell-based and may not contain:
-% - tabs/spacing/line breaks within cells to alter layout or alignment
-% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
-% - colors, shading, or graphic objects
-% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
-%
-% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
-%
-% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
-%
-% IMPORTANT
-% Below are a few tips to help format your equations and other special characters according to our specifications.
-For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
-%
-% Please be sure to include all portions of an equation in the math environment.
-%
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
-%
-% Please add line breaks to long display equations when possible in order to fit size of the column. 
-%
-% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
-%
-% % % % % % % % % % % % % % % % % % % % % % % % 
-%
-% Please contact latex@plos.org with any questions.
-%
-% % % % % % % % % % % % % % % % % % % % % % % %
+\documentclass[]{article}
 
-\documentclass[10pt,letterpaper]{article}
-\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}
+\usepackage{graphicx}
 
-% Use adjustwidth environment to exceed column width (see example table in text)
-\usepackage{changepage}
-
-% Use Unicode characters when possible
-\usepackage[utf8]{inputenc}
-
-% textcomp package and marvosym package for additional characters
-\usepackage{textcomp,marvosym}
-
-% fixltx2e package for \textsubscript
-\usepackage{fixltx2e}
-
-% amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
-\usepackage[version=3]{mhchem}  % added by author
-
-% cite package, to clean up citations in the main text. Do not remove.
-\usepackage{cite}
-
-% Use nameref to cite supporting information files (see Supporting Information section for more info)
-\usepackage{nameref,hyperref}
-
-% line numbers
-\usepackage[right]{lineno}
-
-% ligatures disabled
-\usepackage{microtype}
-\DisableLigatures[f]{encoding = *, family = * }
-
-% rotating package for sideways tables
-\usepackage{rotating}
-
-% Remove comment for double spacing
-%\usepackage{setspace} 
-%\doublespacing
-
-% Text layout
-\raggedright
-\setlength{\parindent}{0.5cm}
-\textwidth 5.25in 
-\textheight 8.75in
-
-% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
-% Captions will be left justified
-\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
-
-% Use the PLoS provided BiBTeX style
-\bibliographystyle{plos2015}
-
-% Remove brackets from numbering in List of References
-\makeatletter
-\renewcommand{\@biblabel}[1]{\quad#1.}
-\makeatother
-
-% Leave date blank
-\date{}
-
-% Header and Footer with logo
-\usepackage{lastpage,fancyhdr,graphicx}
-\usepackage{epstopdf}
-\pagestyle{myheadings}
-\pagestyle{fancy}
-\fancyhf{}
-\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
-\rfoot{\thepage/\pageref{LastPage}}
-\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
-\fancyheadoffset[L]{2.25in}
-\fancyfootoffset[L]{2.25in}
-\lfoot{\sf PLOS}
-
-%% Include all macros below
-
-\newcommand{\lorem}{{\bf LOREM}}
-\newcommand{\ipsum}{{\bf IPSUM}}
-
-%% END MACROS SECTION
+%opening
+\title{Figures for  3-D printed oxygen devices}
+\author{}
 
 \begin{document}
-\vspace*{0.35in}
 
-% Title must be 250 characters or less.
-% Please capitalize all terms in the title except conjunctions, prepositions, and articles.
-\begin{flushleft}
-{\Large
-\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device - Submission to PLOS ONE}
-}
-\newline
-% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
-\\
-Martin D. Brennan\textsuperscript{1},
-Megan L. Rexius-Hall\textsuperscript{1},
-David T. Eddington\textsuperscript{1,*},
-\\
-\bigskip
-\bf{1} Dept of Bioengineering, University of Illinois at Chicago, Chicago, Illinois, USA
-\\
-\bigskip
+%\maketitle
 
-% Use the asterisk to denote corresponding authorship and provide email address in note below.
-* dte@uic.edu
+\section{figures}
 
-\end{flushleft}
-% Please keep the abstract below 300 words
-\section*{Abstract}
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to oxygen-impermeable materials.
-We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D-printed microfluidic devices as a means to enable oxygen control cell culture studies.
-The incorporation of a 3D-printed device and gas-permeable membranes was demonstrated on a 24-well oxygen control device for standard multiwell plates.
-The direct printing allows integrated distribution channels and device geometries not possible with traditional planar lithography.
-With this device, four different oxygen conditions were able to be controlled, and six wells were maintained under each oxygen condition. 
-We demonstrate enhanced transcription of the gene VEGFA (vascular endothelial growth factor A) with decreasing oxygen levels in human lung adenocarcinoma cells.
-This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
-
-\linenumbers
-
-\section*{Introduction}
-Here we report on the development of 3D-printed microfluidic devices for the control of oxygen in cell culture microenvironments.
-We demonstrate a device that nests into a 24-well culture plate to control gas in each row of the plate independently of the incubator's condition.
-This expands on our previous work of a device fabricated using PDMS molds and planar lithography for 6-well plates\cite{Oppegard2009,Oppegard2010}.
-The ability to independently control oxygen across each row of the plate enables more efficient experiments as a separate incubator or hypoxic chamber is not needed for each condition.
-
-3D printing of microfluidic devices enables rapid, one-step fabrication of complex designs infeasible to make with planar lithography and replica molding techniques\cite{Waldbaur2011,Chen2014a}.
-In addition, planar lithography is time consuming, requires specialized equipment and facilities, and has a high failure rate.
-It is not unusual for microfluidic labs to make ten microfluidic devices to guarantee one will work properly.
-On the other hand, 3D CAD printing allows for unambiguous specifications and nearly eliminates time and effort spent on fabrication which may be outsourced to a 3D printing company for around \$200/device \cite{Au2014}.
-3D printing also allows integration of complex geometries not possible with planar lithography, such as hose barbs and luer fittings.
-Dissemination and distributed production is also vastly simplified due to easy sharing of the design as a CAD file.
-Due to these inherent advantages 3D printing has emerged as a method for directly printing complete microfluidic devices \cite{Au2014,Comina2014, Chen2014,Shallan2014,Bhargava2014}. 
-Many prototypical microfluidic device features have been recreated with 3D printing as a proof of concept for this new fabrication technique \cite{ Au2014, Shallan2014} including modular re-configurable units\cite{Yuen2008,Bhargava2014,Lee2014}.
-3D printed devices have been used for neuroengineering applications\cite{Tek2008}, inexpensive and high-throughput reactionware,\cite{Kitson2012,Symes2012,Kitson2013,Kitson2014}, culturing and imaging arrays of seedlings\cite{Busch2012}, measuring dopamine and ATP levels in biological samples with an integrated electrode\cite{Erkal2014}, or plate reader\cite{Chen2014}, and a bacteria separation flow assay\cite{Lee2014a,Lee2015}.
-Other 3D-printed fluidic devices include pneumatic valves\cite{Au2015} a custom NMR cell\cite{Causier2015}, a rapid reconstitution package for lyophilized drugs\cite{Chi2014} and flow plates for a water electrolysis system\cite{Chisholm2014}.
-
-Printing is currently limited in choice of substrate compatible with the 3D printing process.
-Substrate options include many proprietary formulations which have been successfully used in a variety of applications.
-New techniques for using 3D-printed molds to produce devices\cite{Mcdonald2002,Gregory2013,King2014,Comina2014a,Kamei2015} are also being developed, including fugitive ink methods\cite{Therriault2003,Miller2012,Bhargava2015}.
-To date, there are no widely available methods or materials to facilitate direct printing of gas-permeable materials, although this area is actively being explored\cite{Femmer2014a}.
-Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to its biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
-
-Oxygen control in cells studies is often overlooked by researchers, but important for mimicking conditions experienced by cells in vivo.
-Typically cell culture studies are performed at 21\% oxygen, atmospheric oxygen conditions, although levels that cells experience in vivo are less than 21\% \cite{Brennan2014}.
-For example, tumors are generally hypoxic as cancer cells rapidly outgrow their vasculature creating a poorly perfused, hypoxic inner region\cite{Kumar2014}.
-Studying cancer cells under controlled hypoxic conditions is important in understanding the pathophysiology because research has shown hypoxia may enhance aggressive phenotypes, tumor progression, metastasis, and resistance to therapy\cite{Vaupel2004,Vaupel2007,Gilkes2014}.
-Hypoxia is known to alter the transcription of many genes which are under the activity of the HIF (hypoxia inducible factor) family of transcriptional factors\cite{Ke2006,Semenza1999,Semenza2002}.
-To better study the role of oxygen levels in cancer gene expression, a gas controlled culture system is required.
-
-Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the shelf well plate \cite{Oppegard2009, Oppegard2010}.
-These devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
-In addition, tubing was used to connect each pillar which became quite cumbersome when moving to a newer 24-well version.
-Utilizing 3D printing for the fabrication allowed further features to be incorporated such as integrated distribution channels to eliminate the connection tubings between wells and hose barbs for better tubing connections, while eliminating fabrication time and failure rate.
-Although available 3D printable materials are gas-impermeable, the addition of a PDMS membrane following printing of the passive microfluidic network is a simple addition allowing gas transfer. 
-In this case, having a gas-impermeable material for the bulk is advantageous as it reduces unwanted gas transfer from the bulk material prior to the gas exchange interface.
-The previous PDMS devices were Parylene coated along the convection channels to eliminate exchange of gas from the PDMS bulk, which again added to their complexity and is no longer needed.
-Convection and distribution of the gas is done in the impermeable material, eliminating dilution of the gas before reaching the diffusion layer.
-
-% You may title this section "Methods" or "Models". 
-% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
-% authors may use "Analysis" 
-\section*{Materials and Methods}
-\subsection*{Design of insert}
-
-The device was designed to integrate with a multiwell format, specifically an off-the-shelf 24-well plate. 
-The 24-well plate insert was designed to control gas in 4 rows of 6 wells each. 
-Each of the 4 rows can be controlled independently from an input and also incorporates an integrated distribution network and hose barbs to simplify device operation.
-The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
-Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 
-A distribution network stems from the central input that equalizes the flow along each path length by varying the channel width to the proximal, intermediate, and distal wells (Fig.~\ref{fig1}).
-The device also features a pipe within a pipe design so that gas flow enters and leaves the diffusion area in a uniform, and symmetrical flow pattern, which would not be possible with standard lithography and demonstrates the capabilities of 3D printing (Fig.~\ref{fig1}).
-
-\begin{figure}[h]
+\begin{figure}[H]
+\includegraphics[scale=.75]{Fig1.png} 
 \caption{
@@
 }
-\label{fig1}
+\label{figure1}
 \end{figure}
 
-\subsection*{Fabrication of the insert}
-
-CAD models were designed in Autodesk and Blender and printed via stereolithography in Watershed XC by Fineline Prototyping.
-The 3D part contained the microfluidic delivery channels, and was completed by adhering a gas-permeable membrane of PDMS to enable diffusion of gas to the culture area. 
-The PDMS membranes were fabricated by spin coating 10:1 PDMS (Sylgard 184) on a silicon wafer at 900 RPM to a thickness of $\sim$100 $\mu$m and curing at $70\,^{\circ}$C for 30 minutes.
-The PDMS membrane was cut to size and attached to the 3D-printed network with an additional, thin layer of PDMS that was applied as an adhesive to the membrane, secured in position on the end of each pillar, and allowed to cure in place.
-
-\subsection*{Oxygen characterization}
-
-Oxygen was measured with PtOEPK (Pt(II) Octaethylporphine ketone) planar sensors that were fixed to the bottom of a 24-well plate.
-Sensors were prepared as discussed previously \cite{Sinkala2010,Rexius-Hall2014}. 
-Briefly, polystyrene was dissolved in toluene to form a solution to which PtOEPK (Frontier Scientific) was mixed in before spin coating to a thin layer and allowing the toluene to evaporate.
-The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis.
-
-Gas was pulled through the device with negative pressure as a precaution to avoid bulging or detaching membranes, as well as bubble formation in the culture media.
-The outlet ports were connected to a water aspirator which pulled gas through the device from the inlet ports via a flow meter (FL-5311G; Omega) set at 50 ccm.
-The inlet tubing was placed in an open cone that was flooded with gas from a tank with a flow rate of 30 ccm which exceed the vacuum flow rate (12.5 ccm per 6-well network) so that the gas of interest was pulled into the inlet rather than room air due to the open connection.
-In this way, the pressure, and therefore flow rate, was equal across the 4 networks without having to balance flow from 4 pressurized sources, yet different gases of interest can be perfused via vacuum.
-
-Initially the inlets are fed with a 5\% \ce{CO2}, balanced air tank until the intensity stabilized.
-The inlets were then switched to the control gas of either 0, 5, 10, or 21\% \ce{O2}, each with 5\% \ce{CO2} and balanced with \ce{N2}.
-Intensity measurements were then taken every five minutes for six hours.
-All gas tanks used in the oxygen characterization were 5\% \ce{CO2}  in addition to the desired gas mix in anticipation of cell culture experiments (where \ce{CO2} is necessary to buffer the culture media) as \ce{CO2} can alter the fluorescence of the PtOEPK.
-The this entire procedure was repeated three independent times.
-
-\subsection*{Cell culture}
-
-Human lung adenocarcinoma (A549) cells were seeded at 30,000 cells per well in a 24-well plate.
-Cells were cultured in DMEM supplemented with 10\% FBS.
-After reaching $\sim$70\% confluency, the 24-well insert was placed in the plate and the gases were perfused through the device in the same scheme as in the oxygen characterization.
-Each row of six wells experienced either 0\%, 5\%, 10\% or 21\% \ce{O2}, with 5\% \ce{CO2} and balanced nitrogen.
-The assembly was placed in an incubator at $37\,^{\circ}$C for six hours.
-
-\subsection*{Quantitative PCR}
-
-Following six hours of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
-Cells in each well were washed twice with PBS, and 300 $\mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
-The lysate from each well was collected as a sample.
-RNA was extracted according to the PureLink RNA Mini Kit manufacturer’s instructions.
-
-Synthesis of cDNA was performed using the High-Capacity cDNA Reverse Transcription Kit (Applied Biosystems), and quantitative PCR was carried out on ABI PRISM 700O (Applied Biosystems) in 25 $\mu$L reactions using Taqman Gene Expression Assays.
-Beta-2-microglobulin (B2M) served as the endogenous control for calculations of relative gene expression.
-Six technical replicates from the 6-well control unit were processed for each of four oxygen conditions (0\%, 5\%, 10\% and 21\% \ce{O2}) in three independent experiments.
-
-\subsection*{Statistical analysis}
-
-Cell culture experiments were repeated three independent times.
-Data are expressed as the mean $\pm$ SD.
-One-way ANOVA with Tukey’s multiple comparison post-test performed by Prism 5 (Graphpad) determined significance.
-
-% For figure citations, please use "Fig." instead of "Figure".
-%Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
-
-%\begin{enumerate}
-%\item{react}
-%\item{diffuse free particles}
-%\item{increment time by dt and go to 1}
-%\end{enumerate}
-
-% Results and Discussion can be combined.
-\section*{Results}
-\subsection*{Oxygen control}
-Oxygen control in the 24-well insert device was quantified with a platinum-based (PtOEPK) planar oxygen sensor placed at the bottom of the well, as shown in Fig.~\ref{fig2}.
-The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device. 
-A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24-well plate (Fig.~\ref{fig2}).
-There was little variation in the oxygen levels measured in each of the 6 wells controlled by a single inlet, demonstrating the distribution network worked effectively.
-
-\begin{figure}[h]
+\begin{figure}[H]
+\includegraphics[scale=0.2]{Fig2.png}
 \caption{
@@
 }
-\label{fig2}
+\label{figure2}
 \end{figure}
 
-\subsection*{Bioverifcation}
-
-Oxygen levels of 21\%, 10\%, 5\%, and 0\% were applied to each set of 6 wells in which A549 cells were cultured.
-Measurement of relative gene expression confirmed biological responsiveness of cells under the device’s control.
-The device’s ability to control the gas environment was demonstrated with hypoxia-induced upregulation of VEGFA mRNA in the A549 cells (Fig.~\ref{fig3}).
-Quantitative PCR showed a significant increase in the relative gene expression of VEGFA in wells exposed to 0\% \ce{O2} for 6 hours as compared to 21\% \ce{O2}.
-Hypoxia-induced alterations in gene expression usually indicate a HIF-transduced hypoxic signal in cells.
-When a HIF transcription factor undergoes nuclear translocation, it can initiate transcription of genes by binding to the hypoxia response element (HRE)\cite{Lee2004} on its target genes.
-VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions\cite{RohrerBley2011}.
-
-\begin{figure}[h]
+\begin{figure}[H]
+\includegraphics[scale=0.6]{Fig3.png}
 \caption{
@@
 }
-\label{fig3}
+\label{figure3}
 \end{figure}
 
-\subsection*{Discussion}
-This new iteration of the multi-well insert for oxygen control maintains the convenient features of the previous design while improving distribution and interfacing with tubing due to the 3D-printed element.
-Oxygen control is performed in an off-the-shelf culture plate allowing standard protocols to be used for analysis assays or imaging where additional protocols are often required when cells are seeded within microfluidic chips.
-The VEGFA gene expression in A549 cells confirms a biological response using the multi-well insert.
+%\begin{abstract}
 
-This 3D-printed device improves on our previous design in a number of ways.
-First, the fabrication is greatly simplified. 
-No microfabrication, PDMS molding or Parylene coating is required.
-Additionally, the non-permanent adhesion of membranes to the 3D-part allow them to be removed and replaced if they are damaged.
-In PDMS devices the layers are bonded permanently via plasma bonding so damage to a membrane is not repairable.
-3D-printing also enables higher levels of intricacy without any additional fabrication, allowing us to include the distribution network, overlapping of channels in the z-axis, and the 'pipe within a pipe' design.
-A comparable PDMS device would require several additional microfabricated layers to be manually aligned to reproduce just the distribution network.
+%\end{abstract}
 
-Moving forward with additive manufacturing of microfluidic devices is desirable as it will enable highly integrated designs without any additional fabrication.
-For this device an in-device gas mixer could allow more conditions in a single plate, perhaps even one per well or even gradients within wells while reducing the number of gas tanks required as inputs.
-This design could also be applied to higher format plates such as 96-well plates.
-
-\section*{Conclusion}
-3D printing microfluidic chips have been limited to oxygen-impermeable materials.
-We demonstrate oxygen control in 3D-printed devices with the addition of a gas permeable PDMS membrane. 
-Oxygen control is demonstrated in a 24-well plate and PCR detection of upregulation of VEGFA mRNA in A549 cells shows the device effectively controls oxygen as expected. 
-3D printing allows complex designs, integrated tubing connectors, and is comparable in price to standard PDMS fabrication. 
-This technique represents a bridge to commercialization where robust devices can be more easily shared and disseminated. 
-While injection molding, hot embossing, or other industrial processes are cheaper when making hundreds to thousands of devices, it is not practical to make an injection mold when making tens to hundreds of devices.
-In addition, PDMS fabrication would be too time consuming, expensive, and the failure rate would be unacceptable. 3D printing is an excellent solution to these device fabrication needs.
-
-%\begin{table}[!ht]
-%\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%\caption{
-%{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%\begin{tabular}{|l|l|l|l|l|l|l|l|}
-%\hline
-%\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ %\hline
-%$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ %\hline
-%$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ %\hline
-%\end{tabular}
-%\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec %pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%\end{flushleft}
-%\label{table1}
-%\end{adjustwidth}
-%\end{table}
-
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}. 
-%For more information, see \nameref{S1_Text}.
-
-%\section*{Supporting Information}
-
-% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
-%\subsection*{S1 Video}
-%\label{S1_Video}
-%{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-%Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur %pellentesque.
-
-%\subsection*{S1 Text}
-%\label{S1_Text}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur %pellentesque.
-
-%\subsection*{S1 Fig}
-%\label{S1_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur %pellentesque.
-
-%\subsection*{S2 Fig}
-%\label{S2_Fig}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur %pellentesque.
-
-%\subsection*{S1 Table}
-%\label{S1_Table}
-%{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac %ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur %pellentesque.
-
-\section*{Acknowledgments}
-%This work funded by NSF 1253060.
-
-\nolinenumbers
-
-%\section*{References}
-\bibliographystyle{plos2015.bst}
-\bibliography{references}
+%\section{}
 

### 2015-06-23 publishing/latex/revision/revision.tex
organized for tracking changes

--- 2015-06-23 publishing/latex/revision.tex
@@
 {\Large
-\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device - Submission to PLOS ONE}
+\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device}
 }
@@
 \section*{Abstract}
-Recently 3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to oxygen-impermeable materials.
+3D printing has emerged as a method for directly printing complete microfluidic devices, although printing materials have been limited to oxygen-impermeable materials.
 We demonstrate the addition of gas permeable PDMS (Polydimethylsiloxane) membranes to 3D-printed microfluidic devices as a means to enable oxygen control cell culture studies.
@@
 This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
+This is a test of something I'm adding
 

### 2015-06-30 publishing/response-to-reviewers.md
responses to first reviewer

@@
 
-Authors' rebuttal:
+**Authors' rebuttal:** An overview of improvements from our previous PDMS cast devices starts on line 51 of the original manuscript.
 
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:** 
+The work by Kamei et al. was cited along with several other papers that used 3D printed parts as molds for PDMS devices on line 33 of the original manuscript.
 
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:** 
+The wording was changed to "This is the first 3D-printed device that *has been* functionalized to control oxygen in cell culture"
 

### 2015-07-01 publishing/response-to-reviewers.md
changed abstract statement and added volume

@@
 **Authors' rebuttal:** 
-The wording was changed to "This is the first 3D-printed device that *has been* functionalized to control oxygen in cell culture"
+The wording was changed to "This is first 3D-printed device incorporating gas permeable membranes to facilitate oxygen control in cell culture."
 
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:**
+A sentence was added including the approximate volume of media in the gap.
 
@@
 
-Authors' rebuttal: VEGFA is under the transcriptional activity of HIF-1alpha.
+**Authors' rebuttal:** VEGFA is under the transcriptional activity of HIF-1alpha.
 HIF protein peaks at 4 hr, and so we looked at a time point slightly delayed.

### 2015-07-01 publishing/latex/revision/revision.tex
responses to first reviewer
changed abstract statement and added volume

@@
 We demonstrate enhanced transcription of the gene VEGFA (vascular endothelial growth factor A) with decreasing oxygen levels in human lung adenocarcinoma cells.
-This is the first 3D-printed device that can be functionalized to control oxygen in cell culture.
-This is a test of something I'm adding
-
+This is first 3D-printed device incorporating gas permeable membranes to facilitate oxygen control in cell culture.
 \linenumbers
@@
 Each of the 4 rows can be controlled independently from an input and also incorporates an integrated distribution network and hose barbs to simplify device operation.
-The pillars extend into each well leaving a $\sim$500 $\mu$m gap for media between the diffusion membrane and the culture surface at the bottom of the well.
+The pillars extend into each well leaving a $\sim$500 $\mu$m gap between the diffusion membrane and the culture surface.
+This gap allows space for $\sim$0.17 mL of media.
 Diffusion occurs rapidly across this gap allowing control of the dissolved gas environment around the cells. 

### 2015-08-10 data/150807/sternvolmer.m
added data

@@ -1,0 +1,74 @@
+clear
+filename = 'results.txt';
+delimiterIn = '\t';
+headerlinesIn = 1;
+A = importdata(filename,delimiterIn,headerlinesIn);
+intensities = A.data(:, 3);
+M = size(intensities,1)/24;
+wells = reshape(intensities,M,24);
+%csvwrite('wells.csv',wells)
+number_of_calibration_points = 5;
+exposures_per_calibration = 5;
+calibration_exposures = wells(1:[number_of_calibration_points*exposures_per_calibration],:);
+calibration = zeros(number_of_calibration_points,24);
+start = 1;
+last = exposures_per_calibration;
+
+for n = 1:number_of_calibration_points
+   m = calibration_exposures(start:last,:);
+   calibration(n,:) = mean(m);
+   start = last+1;
+   last = last+exposures_per_calibration;
+end
+
+csvwrite('calibration-intensities.csv',calibration)
+exp = wells(number_of_calibration_points*exposures_per_calibration+1:length(wells),:);
+csvwrite('characterization-intensities.csv',exp)
+%%% Stern-Volmer
+calibration_tanks = [0, 1, 7.5, 15, 21];
+I1 = calibration(1,:);
+I2 = calibration(number_of_calibration_points,:);
+X1 = calibration_tanks(1);
+X2 = calibration_tanks(number_of_calibration_points);
+kt = (I2-I1)./((X1*I1)-(X2*I2)); % calculation for Ktau
+Io = I1;
+x1 = [0:1:25]'; % makes x values for plot of stern-volmer
+%stern_volmer_plot = x1*kt+1; % plots I0/I Vs oxygen
+%intensity_plot = I0./(1+kt*x1); % plots intensity(I) Vs oxygen
+
+for i = 1:24
+    oxygen_percent(:,i) = ((Io(i)./exp(:,i))-1)/kt(i);
+end
+
+%%% Two-Site Stern-Volmer fitting
+Q = calibration_tanks';
+for i = 1:24
+    I = calibration(:,i);
+    I0 = I1(i);
[…]

### 2015-08-10 data/sternvolmer.m

@@ -1,82 +1,0 @@
-clear
-load data.csv % data.csv is a single column of intensity data, with the first 4 elements as the two calibration points and corresponding concentration.
-
-intensity_data=data; % enters loaded data into new matrix
-
-I1 = intensity_data(1); % this defines the calibration data based on the element position.
-X1 = intensity_data(2); % in the test-data elements 1 and 2 are the zero percent calibration point.
-I2 = intensity_data(3); % elements 3 and 4 are the 21-percent calibration point.
-X2 = intensity_data(4);
-
-
-kt = (I2-I1)/((X1*I1)-(X2*I2)); % calculation for Ktau
-I0 = (1+kt*X1)*I1;              % intensity in absence of quencher(0% O2)
-
-x1 = 0:1:25; % makes x values for plot of stern-volmer
-
-stern_volmer_plot = x1*kt+1; % plots I0/I Vs oxygen
-intensity_plot = I0./(1+kt*x1); % plots intensity(I) Vs oxygen
-
-I = intensity_data(5:length(intensity_data),:); % makes new matrix with only intensity data
-oxygen_percent = ((I0./I)-1)/kt;
-
-% plotting for standard S-V
-subplot (2, 1, 1)
-[hAx,hline1,hline2] = plotyy(x1,intensity_plot,x1,stern_volmer_plot);
-hline1.Color = 'r';
-hline2.Color = 'b';
-title('Standard Stern-Volmer and Intensity Plot')
-xlabel('% O2')
-ylabel(hAx(1),'intensity') % left axis
-ylabel(hAx(2),'kt*X+1') % right axis
-
-% plotting oxygen percent
-subplot(2, 1, 2)
-plot(oxygen_percent)
-title('Oxygen for Standard Stern-Volmer')
-
-xlabel('time')
-ylabel('% O2')
-
-
-%%%%%%%%%%%%%%%%%%%% TWO-SITE MODEL
-
-f1 =   0.9245;
-f2 = 1-f1;
-ksv1 = 0.1513;
-ksv2 = 7.357e-10;
-
-% Solving for Q
[…]

### 2015-08-10 data/system_solver.m

@@ -1,22 +1,0 @@
-clear
-
-syms f1 f2 ksv1 ksv2 clear
-
-% (f1/(1+ksv1*Q))+(f2/(1+ksv2*Q))== I/I0
-
-I0 = 2376.4;
-Ione = 2148.6; % from analyzed data
-Q1 = 1;
-I10 = 1000.8;
-Q10 = 10;
-I21 = 736.52;
-Q21 = 21;
-
-eq1=(f1/(1+Q1*ksv1))+(f2/(1+Q1*ksv2))==(Ione/I0);
-eq2=(f1/(1+Q10*ksv1))+(f2/(1+Q10*ksv2))==(I10/I0);  
-eq3=(f1/(1+Q21*ksv1))+(f2/(1+Q21*ksv2))==(I21/I0);
-eq4= f1 + f2 == 1;
-
-%solve([x^2+y == 5, x^2+y^2 == 7],[x, y])
-
-[solf1, solf2, solksv1, solksv2] = vpasolve([eq1, eq2, eq3, eq4], [f1, f2, ksv1, ksv2])

### 2015-08-11 data/plotting.R
working on plotting

@@ -1,0 +1,12 @@
+oxygen_average <- read.csv(file='average.csv', sep=',', header=FALSE)
+A <- seq(from = 0, to = (72*5), by = 5)
+A <- (A/60)
+matplot(A, oxygen_average, type = "l", pch=1, lty=1, col = 1:6, axes=F, ann=F, ylim=c(0,25))
+#legend("topright", legend = 1:24, col=1:6, pch=1)
+title(ylab="Oxygen Concentration (%)", xlab="Time (hours)")
+axis(1)
+axis(2)
+std <- read.csv(file='std.csv', sep=',', header=FALSE)
+arrows(A, oxygen_average$V1-std$v1, length=0.05, angle=90, code=3)
+plot(A, oxygen_average$V1)
+arrows(A, oxygen_average$V1-std$v1, length=0.05, angle=90, code=3)

### 2015-08-11 data/average.m
fixed std output

@@ -10,6 +10,6 @@ A(:,:,2)= csvread('analyzed-oxygen-values-150807.csv');
 ave = mean(A,3);
 csvwrite('average.csv',ave)
 S = std(A,0,3);
-csvwrite('std.csv',ave)
+csvwrite('std.csv',S)
 %plot(ave)
 errorbar(ave,S)

### 2015-08-13 data/150812/sternvolmer.m
n3 added

@@ -71,4 +71,4 @@ end
 plot(oxygen_percent_twosite,'b-')
 hold on
 plot(oxygen_percent,'r--')
-csvwrite('analyzed-oxygen-values-150805.csv',oxygen_percent_twosite)
+csvwrite('analyzed-oxygen-values-150812.csv',oxygen_percent_twosite)

### 2015-08-13 data/average.m

@@ -3,13 +3,13 @@ clear
 %N2 = csvread('analyzed-oxygen-values-150807.csv');
 %N3 = csvread('analyzed-oxygen-values-150808.csv');
 
-A = zeros(73,24,2);
+A = zeros(73,24,3);
 A(:,:,1)= csvread('analyzed-oxygen-values-150805.csv');
 A(:,:,2)= csvread('analyzed-oxygen-values-150807.csv');
-%A(:,:,2)= csvread('analyzed-oxygen-values-150808.csv');
+A(:,:,3)= csvread('analyzed-oxygen-values-150812.csv');
 ave = mean(A,3);
 csvwrite('average.csv',ave)
 S = std(A,0,3);
 csvwrite('std.csv',S)
-%plot(ave)
-errorbar(ave,S)
+plot(ave)
+%errorbar(ave,S)

### 2015-08-13 publishing/response-to-reviewers.md
exported plots

@@
 Thank you for reviewing our manuscript submission to PLOS ONE. We have made several improvements and clarifications resulting what we hope is a stronger manuscript ready for publication.
-
-If you would like to make changes to your financial disclosure, please include your updated statement in your cover letter.
 
@@
 
-**Authors' rebuttal:** An overview of improvements from our previous PDMS cast devices starts on line 51 of the original manuscript.
+**Authors' rebuttal:** 
+An overview of improvements from our previous PDMS cast devices starts on line 51 of the original manuscript.
 
@@
 
-**Authors' rebuttal:** VEGFA is under the transcriptional activity of HIF-1alpha.
+**Authors' rebuttal:** 
+VEGFA is under the transcriptional activity of HIF-1alpha.
 HIF protein peaks at 4 hr, and so we looked at a time point slightly delayed.
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:**
+The data in the original submission was analyzed with a two point calibration.
+This method correlates intensites to oxygen concentration assuming a linear Stern-Volmer relationship.
+While standard practice, the two-point calibration suffers from increasing inaacuracy as points are measured further away from the calibration points.
 

### 2015-08-13 data/plotting.R
saved plotting

@@ -3,9 +3,24 @@ A <- seq(from = 0, to = (72*5), by = 5)
 A <- (A/60)
 matplot(A, oxygen_average, type = "l", pch=1, lty=1, col = 1:6, axes=F, ann=F, ylim=c(0,25))
 #legend("topright", legend = 1:24, col=1:6, pch=1)
-title(ylab="Oxygen Concentration (%)", xlab="Time (hours)")
-axis(1)
-axis(2)
+axis(1, cex.axis=1.2)
+axis(2, cex.axis=1.2)
+title(ylab="Oxygen Concentration (%)", xlab="Time (hours)", cex.lab=1.5)
 std <- read.csv(file='std.csv', sep=',', header=FALSE)
-for ( i in seq(1,length( std ),1) ) arrows(A, oxygen_average[,i]-std[,i], A, oxygen_average[,i]+std[,i], length=0.05, angle=90, code=3)
-arrows(A, oxygen_average$V1-std$V1, A, oxygen_average$V1+std$V1, length=0.0, angle=90, code=3)
+for ( i in seq(1,length( std ),1) ) arrows(A, oxygen_average[,i]-std[,i], A, oxygen_average[,i]+std[,i], length=0.03, angle=90, code=3)
+
+row1_range <- paste("V", 1:6, sep="")
+row1 <- oxygen_average[row1_range]
+row2_range <- paste("V", 7:12, sep="")
+row2 <- oxygen_average[row2_range]
+row3_range <- paste("V", 13:18, sep="")
+row3 <- oxygen_average[row3_range]
+row4_range <- paste("V", 19:24, sep="")
+row4 <- oxygen_average[row4_range]
+
+matplot(A, row2, type = "l", pch=1, lty=1, col = 1:6, axes=F, ann=F, ylim=c(0,25))
+legend("topright", c("well 1","well 2","well 3","well 4","well 5", "well 6"), col=1:6, lty=1, )
+axis(1, cex.axis=1.2)
+axis(2, cex.axis=1.2)
+title(ylab="Oxygen Concentration (%)", xlab="Time (hours)", cex.lab=1.5)
+for ( i in seq(7, 12, 1) ) arrows(A, oxygen_average[,i]-std[,i], A, oxygen_average[,i]+std[,i], length=0.04, angle=90, code=3)

### 2015-08-13 publishing/response-to-reviewers.md
updated response

--- 2015-07-01 publishing/response-to-reviewers.md
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:**
+The data in the original submission was analyzed with a two point calibration.
+This method correlates intensities to oxygen concentration assuming a linear Stern-Volmer relationship.
+While standard practice, the two-point calibration suffers from increasing inaccuracy as points are measured further away from the calibration points.
+Characterization data was re-taken with 5 calibration points and analyzed with a two-site Stern-Volmer model to increase accuracy of analyzed data.
+A new plot replaces figure 2 with error bars.
 
@@
 
-Authors' rebuttal:
+**Authors' rebuttal:**
+We did not observe any contamination.

### 2015-08-13 data/plotting.R
made new plot with error bars

@@ -1,7 +1,8 @@
 oxygen_average <- read.csv(file='average.csv', sep=',', header=FALSE)
 A <- seq(from = 0, to = (72*5), by = 5)
 A <- (A/60)
-matplot(A, oxygen_average, type = "l", pch=1, lty=1, col = 1:6, axes=F, ann=F, ylim=c(0,25))
+
+matplot(A, oxygen_average, type = "l", pch=1, lty=1, lwd = 2, col = 1:6, axes=F, ann=F, ylim=c(0,25))
 #legend("topright", legend = 1:24, col=1:6, pch=1)
 axis(1, cex.axis=1.2)
 axis(2, cex.axis=1.2)

### 2015-08-13 publishing/response-to-reviewers.md
updating manuscript

@@
 Characterization data was re-taken with 5 calibration points and analyzed with a two-site Stern-Volmer model to increase accuracy of analyzed data.
-A new plot replaces figure 2 with error bars.
+A new plot replaces figure 2 and includes error bars.
 
@@
 **Authors' rebuttal:**
+Sterilization was preformed by spraying the device with 70% ethonal and leaving it in a biosaftey hood with UV lights overnight.
 We did not observe any contamination.
+This information was added to the manuscript.

### 2015-08-13 publishing/latex/revision/revision.tex
updating manuscript

@@
 Briefly, polystyrene was dissolved in toluene to form a solution to which PtOEPK (Frontier Scientific) was mixed in before spin coating to a thin layer and allowing the toluene to evaporate.
-The intensity of the sensor was measured with via fluorescence microscopy and correlated to the concentration of oxygen with Stern-Volmer analysis.
+Five calibration points were fitted to a two-site model\cite{Carraway1991,Wang2014} of the Stern-Volmer relationship which was used to correlate sensor intensities with oxygen concentration.
 
@@
 
+The assembled device was sterilized by spraying with 70\% ethanol solution and placed in a biosaftey hood with UV lights overnight.
 Human lung adenocarcinoma (A549) cells were seeded at 30,000 cells per well in a 24-well plate.
@@
 Following six hours of oxygen modulation, the 24-well oxygen control insert was removed and culture media was aspirated.
+No contamination of the culture was observed.
 Cells in each well were washed twice with PBS, and 300 $\mu$L of a lysis solution consisting of 10 $\mu$L of $\beta$-mercaptoethanol (Sigma Aldrich) per 1 mL of lysis buffer (PureLink RNA Mini Kit; Invitrogen) was added to each well.
@@
 The device reaches steady state in 30 minutes and can then hold the oxygen level near 0\% \ce{O2} indefinitely, while 95\% \ce{N2}, 5\% \ce{CO2} is pumped through the device.
-A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24-well plate (Fig.~\ref{fig2}).
+A different gas condition can be used in each separate iteration of the 6-well unit allowing 6 technical replicates of up to 4 different gas conditions in one 24-well plate.
 There was little variation in the oxygen levels measured in each of the 6 wells controlled by a single inlet, demonstrating the distribution network worked effectively.
@@
 {\bf Oxygen Characterization.} 
-(A) Time course data of oxygen being evacuated from the culture area as 0\% oxygen gas is perfused through the device.
+Time course data of four oxygen conditions are demonstrated in a 24-well plate.
+Each 6-well row of the plate can be controlled independently.  
 Error bars are the standard deviation N=3.
-(B) Four oxygen conditions are demonstrated in a 24-well plate.
-Each 6-well row of the plate can be controlled independently.  
-Mean N=3 error bars not included.
 }

### 2015-08-13 publishing/response-to-reviewers.md
updated readme

@@
 PONE-D-15-17915
+
 3D-Printed 24-Well Plate Oxygen Control Device
+
 PLOS ONE
@@
 
-Authors' Rebuttal to Reviewers
+**Authors' Rebuttal to Reviewers:**
 
-Reviewer #1:
+**Reviewer #1:**
+
 It is a different version of design to control oxygen in cell culture, among some recent efforts.
@@
 
-**Authors' rebuttal:** 
-An overview of improvements from our previous PDMS cast devices starts on line 51 of the original manuscript.
+* **Authors' rebuttal:** 
+An overview of improvements from our previous PDMS cast devices starts on line 51 of the original manuscript, now line 64 of the revised manuscript.
 
@@
 
-**Authors' rebuttal:** 
-The work by Kamei et al. was cited along with several other papers that used 3D printed parts as molds for PDMS devices on line 33 of the original manuscript.
+* **Authors' rebuttal:** 
+The work by Kamei et al. was cited along with several other papers that used 3D printed parts as molds for PDMS devices on line 33 of the original manuscript, now line 46 of the revised manuscipt.
 
@@
 
-**Authors' rebuttal:** 
+* **Authors' rebuttal:** 
 The wording was changed to "This is first 3D-printed device incorporating gas permeable membranes to facilitate oxygen control in cell culture."
 
-------------------------------
+**Reviewer #2:**
 
-Reviewer #2:
 Currently, little consideration is given to mimicking physiological oxygen concentrations in vitro during cell experiments.
@@
 Although the concept is interesting, the data is not sufficient and additional experiments are needed to improve the manuscript.
-•	Page 3 - In addition to presenting gap distance below insert and well bottom, it would be helpful if the authors included volume of media this space would hold.
 
-**Authors' rebuttal:**
-A sentence was added including the approximate volume of media in the gap.
+Page 3 - In addition to presenting gap distance below insert and well bottom, it would be helpful if the authors included volume of media this space would hold.
 
-•	Page 4 – Why was 6 hrs chosen for cell culture?
+* **Authors' rebuttal:**
+A sentence was added including the approximate volume of media in the gap. See line 87 of the revised manuscript.
+
+Page 4 – Why was 6 hrs chosen for cell culture?
 It would seem that the authors could demonstrate a more robust change in expression over the concentrations tested if the experiment was extended to a longer time point, especially considering only the 0% group showed a significant difference in VEGFA expression.
 
-**Authors' rebuttal:** 
+* **Authors' rebuttal:** 
 VEGFA is under the transcriptional activity of HIF-1alpha.
@@
 By longer time points, the HIF response is actually suppressed, and many transcripts are not increased with longer time points.
-See Rexius-Hall et al.s' work.
+See Rexius-Hall et al.s' work, citation 44.
 
-•	The authors specify concentrations of 21%, 10%, 5%, and 0% were evaluated, however in their Figure 2b, the concentrations appear closer to 13% (not 10%) and 7% (not 5%).
+The authors specify concentrations of 21%, 10%, 5%, and 0% were evaluated, however in their Figure 2b, the concentrations appear closer to 13% (not 10%) and 7% (not 5%).
 Variation of 3% can be considerable in physiological environments and it is unclear if the authors recognize this variation.
@@
 
-**Authors' rebuttal:**
+* **Authors' rebuttal:**
 The data in the original submission was analyzed with a two point calibration.
@@
 
-•	Is sterilization an issue for this device, considering it will be in close contact with biological components?
+Is sterilization an issue for this device, considering it will be in close contact with biological components?
 
-**Authors' rebuttal:**
+* **Authors' rebuttal:**
 Sterilization was preformed by spraying the device with 70% ethonal and leaving it in a biosaftey hood with UV lights overnight.
@@
 This information was added to the manuscript.
+See lines 131, and 141.

### 2015-08-17 publishing/response-to-reviewers.md
added vegf data

@@
 
-3D-Printed 24-Well Plate Oxygen Control Device
+A 3D-Printed Oxygen Control Insert for a 24-Well Plate
 
@@
 * **Authors' rebuttal:** 
-The work by Kamei et al. was cited along with several other papers that used 3D printed parts as molds for PDMS devices on line 33 of the original manuscript, now line 46 of the revised manuscipt.
+The work by Kamei et al. was cited along with several other papers that used 3D printed parts as molds for PDMS devices on line 33 of the original manuscript, now line 46 of the revised manuscript.
 
@@
 VEGFA is under the transcriptional activity of HIF-1alpha.
-HIF protein peaks at 4 hr, and so we looked at a time point slightly delayed.
-By longer time points, the HIF response is actually suppressed, and many transcripts are not increased with longer time points.
-See Rexius-Hall et al.s' work, citation 44.
+The time course of HIF-1alpha protein levels in A549 cells demonstrates maximal protein levels at 4 h and a steep decrease in expression by 16 h.
+Based on the known time course, we looked at a time point slightly delayed from the 4 h peak to account for transcription of the downstream target gene of interest (VEGFA).
+At longer time points, HIF protein expression is actually suppressed, and many transcripts are not increased with extended duration.
+This additional information was added along with a citation starting at line 182.
 
@@
 * **Authors' rebuttal:**
-Sterilization was preformed by spraying the device with 70% ethonal and leaving it in a biosaftey hood with UV lights overnight.
+Sterilization was preformed by spraying the device with 70% ethanol and leaving it in a biosaftey hood with UV lights overnight.
 We did not observe any contamination.

### 2015-08-17 publishing/latex/revision/revision.tex
added vegf data

@@
 {\Large
-\textbf\newline{3D-Printed 24-Well Plate Oxygen Control Device}
+\textbf\newline{A 3D-Printed Oxygen Control Insert for a 24-Well Plate}
 }
@@
 We demonstrate enhanced transcription of the gene VEGFA (vascular endothelial growth factor A) with decreasing oxygen levels in human lung adenocarcinoma cells.
-This is first 3D-printed device incorporating gas permeable membranes to facilitate oxygen control in cell culture.
+This is the first 3D-printed device incorporating gas permeable membranes to facilitate oxygen control in cell culture.
 \linenumbers
@@
 Microfluidic cell culture devices are most commonly cast in PDMS as it is a convenient material for cell studies due to its biocompatibility, optical properties, and gas permeability, facilitating oxygen control of cell environments\cite{Sia2003,Brennan2014}.
+In this study, a larger 24 well version was developed and optimized which includes several key improvements over the previous 6-well version.
 
@@
 Previously, we developed multiwell inserts for 6-well plates that controlled oxygen in a standard off-the shelf well plate \cite{Oppegard2009, Oppegard2010}.
-These devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
+These 6-well devices were completely cast from PDMS and fabricated in a multiple bonding procedure.
 In addition, tubing was used to connect each pillar which became quite cumbersome when moving to a newer 24-well version.
@@
 VEGFA has previously been shown to have a functional HRE, and upregulation has been observed in A549 cells under hypoxic conditions\cite{RohrerBley2011}.
-
+The 6 h time point was chosen based on the HIF-1$\alpha$ timecourse in A549 cells. 
+HIF-1$\alpha$ protein levels are maximal at 4 h and steeply decrease by 16 h\cite{Li2006}. 
+Based on the known time course, we looked at a time point slightly delayed from the 4 h peak to account for transcription of the downstream target genes.
 \begin{figure}[h]
@@
 
-\section*{Acknowledgments}
+%\section*{Acknowledgments}
 %This work funded by NSF 1253060.
